\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2020-07-06 doc/USER_MANUAL/04_creating_databases.tex
updates doc

\item [{\texttt{gll}}] For a user-specified isotropic model which uses
external binary files for $v_{p}$, $v_{s}$ and $\rho$. Binary files
are given in the same format as when outputted by the \texttt{xgenerate\_databases}
executable when using option \texttt{SAVE\_MESH\_FILES}. These binary
files define the model parameters on all GLL points which can be used
for iterative inversion procedures. Note that for simulation setups with attenuation,
it will also read in the external binary mesh files for $Q_{\kappa}$ and $Q_{\mu}$.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp. To convert one to the other see doc/note\_on\_Qkappa\_versus\_Qp.pdf and utils/attenuation/conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90.

@@

\item [{\texttt{APPROXIMATE\_OCEAN\_LOAD}}] Set to \texttt{.true.} if the
effect of the oceans on seismic wave propagation should be incorporated
based upon the (rough) approximate treatment discussed in \citet{KoTr02b}.
This feature is inexpensive from a numerical perspective, both in
terms of memory requirements and CPU time. This approximation is accurate
at periods of roughly 20~s and longer. At shorter periods the effect
of water phases/reverberations is not taken into account, even when
the flag is on. If you want to model the effect of a fluid-solid model
at short periods, then set this flag to \texttt{.false.} and mesh
the fluid layer explicitly in your mesher, so that it is computed
accurately and without this approximation.
\item [{\texttt{TOPOGRAPHY}}] This feature is only effective if \texttt{APPROXIMATE\_OCEAN\_LOAD}
is set to \texttt{.true.}. Set to \texttt{.true.} if topography and
bathymetry should be read in based upon the topography file specified
in the main constants file \texttt{constants.h} found in subdirectory
\texttt{src/shared/} to evaluate elevations. If not set, elevations
will be read from the numerical mesh.
\item [{\texttt{ATTENUATION}}] Set to \texttt{.true.} if attenuation should
be incorporated. Turning this feature on increases the memory requirements
significantly (roughly by a factor of~1.5), and is numerically fairly
expensive. See \citet{KoTr99,KoTr02a} for a discussion on the implementation
of attenuation based upon standard linear solids. Please note that
the Vp- and Vs-velocities of your model are given for a reference
frequency. To change this reference frequency, you change the value
of \texttt{ATTENUATION\_f0\_REFERENCE} in the main constants file
\texttt{constants.h} found in subdirectory \texttt{src/shared/}.
The code uses a constant $Q$ quality factor, write(IMAIN,*) "but approximated based on a series of Zener standard linear solids (SLS).
The approximation is thus performed in a given frequency band determined based on that \texttt{ATTENUATION\_f0\_REFERENCE} reference frequency.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp.
To convert one to the other see doc/note\_on\_Qkappa\_versus\_Qp.pdf and utils/attenuation/conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90.

>>>>

\item [{\texttt{gll}}] For a user-specified isotropic model which uses
external binary files for $v_{p}$, $v_{s}$ and $\rho$. Binary files
are given in the same format as when outputted by the \texttt{xgenerate\_databases}
executable when using option \texttt{SAVE\_MESH\_FILES}. These binary
files define the model parameters on all GLL points which can be used
for iterative inversion procedures. Note that for simulation setups with attenuation,
it will also read in the external binary mesh files for $Q_{\kappa}$ and $Q_{\mu}$.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp.
To convert one to the other see \texttt{doc/note\_on\_Qkappa\_versus\_Qp.pdf}
and in folder \texttt{utils/attenuation}, the tool
\texttt{conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90}.

@@

\item [{\texttt{APPROXIMATE\_OCEAN\_LOAD}}] Set to \texttt{.true.} if the
effect of the oceans on seismic wave propagation should be incorporated
based upon the (rough) approximate treatment discussed in \citet{KoTr02b}.
This feature is inexpensive from a numerical perspective, both in
terms of memory requirements and CPU time. This approximation is accurate
at periods of roughly 20~s and longer. At shorter periods the effect
of water phases/reverberations is not taken into account, even when
the flag is on. If you want to model the effect of a fluid-solid model
at short periods, then set this flag to \texttt{.false.} and mesh
the fluid layer explicitly in your mesher, so that it is computed
accurately and without this approximation.
\item [{\texttt{TOPOGRAPHY}}] This feature is only effective if \texttt{APPROXIMATE\_OCEAN\_LOAD}
is set to \texttt{.true.}. Set to \texttt{.true.} if topography and
bathymetry should be read in based upon the topography file specified
in the main constants file \texttt{constants.h} found in subdirectory
\texttt{src/shared/} to evaluate elevations. If not set, elevations
will be read from the numerical mesh.
\item [{\texttt{ATTENUATION}}] Set to \texttt{.true.} if attenuation should
be incorporated. Turning this feature on increases the memory requirements
significantly (roughly by a factor of~1.5), and is numerically fairly
expensive. See \citet{KoTr99,KoTr02a} for a discussion on the implementation
of attenuation based upon standard linear solids. Please note that
the Vp- and Vs-velocities of your model are given for a reference
frequency. To change this reference frequency, you change the value
of \texttt{ATTENUATION\_f0\_REFERENCE} in the main constants file
\texttt{constants.h} found in subdirectory \texttt{src/shared/}.
The code uses a constant $Q$ quality factor, write(IMAIN,*) "but approximated based on a series of Zener standard linear solids (SLS).
The approximation is thus performed in a given frequency band determined based on that \texttt{ATTENUATION\_f0\_REFERENCE} reference frequency.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp.
To convert one to the other see \texttt{doc/note\_on\_Qkappa\_versus\_Qp.pdf}
and in folder \texttt{utils/attenuation}, the tool
\texttt{conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90}.
